Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-17 paper/paper.tex
Updates from Overleaf

The analysis in this paper builds upon that of \cite{schoenholzer2022} and extends it by identifying special cases of switching events: in \textit{conquests} a city is forcefully absorbed into a new state, while in \textit{successions} a city is absorbed into a new state after the rulers of the old state have gone extinct. Comparing the effects of these two types of switches allows me to tease out the effect of state power. I find a positive and significant effect of state power on the long-run development of cities. This result suggests that conflict-driven evolution indeed played a role in the rise of Europe relative to other regions of the world.

I make a key assumption: conquests imply state power differentials but successions do not. Specifically, if we consider the universe of all switching events, the average increase in state power from the old to the new owner would be higher for the conquests than for the successions. The reasoning is that conflict --- as in a conquest --- selects the new state for power, but conflict-free successions, depending mainly on dynastic marriages, are more "random". This assumption allows me to use conquests as a stand-in for an increase in state power. Several other assumptions are needed to interpret my results causally, which I will discuss in detail below.

@@

@@

I can barely believe it myself, but I replicate their finding:

@@

\begin{multline}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) +
    \mathbf{1}(t \ge e^{NewState}_i)\beta +
    \mathbf{1}(t \ge e^{NewState}_i) \times C_i \theta + \varepsilon_{it}
\end{multline}

Unfortunately it's not as convincing:

@@

>>>>

The analysis in this paper builds upon that of \cite{schoenholzer2022} and extends it by identifying special cases of switching events: in \textit{conquests} a city is forcefully absorbed into a new state, while in \textit{successions} a city is absorbed into a new state after the rulers of the old state have gone extinct. Comparing the effects of these two types of switches allows me to tease out the effect of state power. Identification is based on the assumption that conquests imply state power differentials but successions do not. Specifically, if we consider the universe of all switching events, the average increase in state power from the old to the new owner would be higher for the conquests than for the successions. The reasoning is that conflict --- as in a conquest --- selects the new state for power, but conflict-free successions, depending mainly on dynastic marriages, are more "random". This assumption allows me to use conquests as a stand-in for an increase in state power. Several other assumptions are needed to interpret my results causally.

While I am able to replicate \cite{schoenholzer2022}'s result that the long-run effect of switching to another state is positive, I fail to identify a statistically significant effect of state power on urban development. This does not necessarily mean that conflict-driven evolution played no role in the rise of Europe --- several issues limit the statistical power of my test, which might prevent me from finding an effect even if there is one. The biggest one is that the data I use is arguably inadequate for answering the research question.

@@

\subsection{Long-run effect of switching}

@@

\subsection{Effect of state power}

@@

I use a triple interaction. I extend the previous regression

\begin{multline}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0) +
    \mathbf{1}(t \ge e^{NewState}_i)\beta +
    \mathbf{1}(t \ge e^{NewState}_i) \times C_i \times \theta + \varepsilon_{it}
\end{multline}

Blah blah.

\section{Results}

I can barely believe it myself, but I replicate their finding. Table 
Figure \ref{fig:SW_replication} shows the dynamic effect of switching. Cities were on average

The it's not as convincing:

@@

\subsection{Tables}

\subsection{Figures}
